Embedding co-affiliation trajectories reveals structure of global scientific mobility

### 2020-01-17 paper/ic2s2-2020/ic2s2_mobility_emb.tex
Fixed double-quote marks

We source bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations from the Web of Science database hosted by Leiden University. 
A "sentence" is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication, as shown in Fig \ref{fig:image}.a for two example authors. 
These sentences are used as input into the standard (\textit{word2vec}) skip-gram model~\autocite{mikolov_distributed_2013}.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.83\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
	\caption{ 
	\textbf{Embedding offer robust model of co-affiliation, reveals multi-scale structure.}
	\textbf{a:} Examples of how "sentences" for the skip-gram model are created from author's affiliations listed on papers.
	\textbf{b:} Relationship between \textit{flux} and embedding similarity stronger than for geographic distance. 
	Red line is line of best fit.
	Black points are the mean flux for each binned by distance or similarity. 
	\textbf{c:} Predicting flux using gravity law.
	Box-plots show distribution of actual flux binned by expected, and color represents the the degree to which the distribution overlaps the line $x = y$. 
	\textbf{d:} Umap projection of embedding space demonstrating geographic clustering or organizations.
	Umap re-projections of subsets of organization vectors vectors for organizations in the United States (\textbf{e}), Massachusetts (\textbf{f.}), Central- and South-East Asia (\textbf{g}) and Central and South-American and Iberian countries (\textbf{h}). 
	 }
	\label{fig:image}
\end{figure}

>>>>

We source bibliographic data on more than 22 million papers published between 2008 and mid 2019, comprising 3.7 million disambiguated authors and 8,445 organizations from the Web of Science database hosted by Leiden University. 
A ``sentence'' is constructed for each author by concatenating organization ids for each affiliation listed on their papers, ordered by year of publication, as shown in Fig \ref{fig:image}.a for two example authors. 
These sentences are used as input into the standard (\textit{word2vec}) skip-gram model~\autocite{mikolov_distributed_2013}.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.83\textwidth]{../Figs/ic2s2-2020/ic2s2_2020_mainfig.pdf}
	\caption{ 
	\textbf{Embedding offer robust model of co-affiliation, reveals multi-scale structure.}
	\textbf{a:} Examples of how ``sentences'' for the skip-gram model are created from author's affiliations listed on papers.
	\textbf{b:} Relationship between \textit{flux} and embedding similarity stronger than for geographic distance. 
	Red line is line of best fit.
	Black points are the mean flux for each binned by distance or similarity. 
	\textbf{c:} Predicting flux using gravity law.
	Box-plots show distribution of actual flux binned by expected, and color represents the the degree to which the distribution overlaps the line $x = y$. 
	\textbf{d:} Umap projection of embedding space demonstrating geographic clustering or organizations.
	Umap re-projections of subsets of organization vectors vectors for organizations in the United States (\textbf{e}), Massachusetts (\textbf{f.}), Central- and South-East Asia (\textbf{g}) and Central and South-American and Iberian countries (\textbf{h}). 
	 }
	\label{fig:image}
\end{figure}
